%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Cover Letter – Guillermo González Martín – 01/2026 %%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}

\geometry{left=2cm,right=2cm,top=1.5cm,bottom=1.5cm}

% Paragraph spacing
\setlength{\parskip}{1em}

\iftutex
  \setmainfont{Roboto Slab}
  \setsansfont{Lato}
  \renewcommand{\familydefault}{\sfdefault}
\else
  \usepackage[rm]{roboto}
  \usepackage[defaultsans]{lato}
  \renewcommand{\familydefault}{\sfdefault}
\fi

\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\definecolor{DarkPastelRed}{HTML}{001F33}
\definecolor{PastelRed}{HTML}{005B8F}
\definecolor{GoldenEarth}{HTML}{7AA9D6}

\colorlet{name}{black}
\colorlet{tagline}{PastelRed}
\colorlet{heading}{DarkPastelRed}
\colorlet{headingrule}{GoldenEarth}
\colorlet{subheading}{PastelRed}
\colorlet{accent}{PastelRed}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\renewcommand{\namefont}{\Huge\rmfamily\bfseries}
\renewcommand{\personalinfofont}{\footnotesize}
\renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}

\begin{document}

\name{Guillermo González Martín}
\tagline{Embedded Software Engineer}

\personalinfo{%
  \email{guille.gonzalez.13@gmail.com}
  \phone{+34 610 24 82 57}
  \location{Madrid, Spain}
  \linkedin{guillegonzzalez}
  \github{guillegonzzalez}
}

\makecvheader

\vspace{0.6cm}

\cvsection{Cover Letter}

\justifying

I am an \textbf{Embedded Software Engineer} with six years of experience developing low-level firmware in \textbf{C}, working closely with \textbf{electrical and electronic systems} in production environments. My background combines hands-on work in startup settings—where I have been deeply involved in hardware bring-up, driver development and system integration—with experience in large industrial organizations, where robustness, process and traceability are critical.

Over the years, I have worked with a \textbf{wide range of microcontrollers and communication protocols}, developing embedded software at the hardware–firmware boundary. My work has included peripheral integration, low-level driver development, debugging complex hardware issues and supporting new board bring-up. In parallel, I have gained experience with \textbf{Linux-based systems}, including basic \textbf{Yocto} usage, in production-oriented contexts where reliability and maintainability are key.

For the past eight months, I have been working as a consultant for \textbf{Airbus}, which has allowed me to gain first-hand experience in large-scale engineering organizations. This role has exposed me to structured development processes, cross-functional collaboration and safety-oriented engineering practices. Having worked in both agile startup environments and highly regulated industrial projects, I am comfortable \textbf{adapting to different development cultures} while maintaining a strong focus on quality, robustness and long-term reliability.

I am genuinely passionate about electronics and electrical systems. I enjoy understanding how complex systems work, troubleshooting issues methodically and continuously expanding my technical knowledge. Outside of my professional work, I actively develop personal projects related to programming and electronics, which helps me deepen my practical understanding beyond day-to-day responsibilities.

\textbf{TK Elevator} particularly interests me due to its strong focus on industrial electrical and electronic systems, safety-critical applications and real-world impact. I believe my background in embedded systems, close interaction with hardware and experience in both industrial and fast-paced environments \textbf{aligns very well} with the challenges of this role.

I am currently looking for a hybrid position close to home, with a compensation range starting at \textbf{€50–55k}. My availability would be approximately \textbf{one month after acceptance}. I would welcome the opportunity to further discuss how my experience and interests could contribute to your team.

\vspace{0.8cm}

Kind regards,\\[0.2cm]
\textbf{Guillermo González Martín}

\end{document}
